---
title: "Problem Set 1"
author: "Zack Renick"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("/Users/econgrad/Documents/Econ_294A/data"))
```

#Problem 1
```{r}
ETH_USD <- read.csv('ETH-USD.csv')
summary(ETH_USD[c('Open', 'Close', 'High', 'Low', 'Adj.Close' , 'Volume')])

#Solution
library(knitr)
sum_fun = function(x)
{
r = lapply(ETH_USD[,2:7], summary)
r = do.call("rbind",r)
r = data.frame(r)
colnames(r) = c('Min','Q1','Median','Mean','Q3','Max')
rownames(r) = c('Open','High','Low','Close','Adj.Close','Volume')
r = round(r,2)
return(r)
}
r1 = sum_fun(ETH_USD)
kable(r1,caption='Summary statistics')

#Testing sapply to directly create a matrix
r2 = sapply(ETH_USD[,2:7], summary)
r2 = round(r2,2)
kable(r2,caption='Summary statistics')
```
#Problem 2
```{r}
trading_volume <- function(start,end){
  new_data = ETH_USD[ETH_USD$Date >= start & ETH_USD$Date <= end,]
  a = mean(new_data$Volume)
  b = sd(new_data$Volume)
  d = b / a * 100
  return(c(a,b,d))
  return(list(a,b,d))
}
x <- as.Date(readline(prompt = "Enter the start date as YYYY-MM-DD."))
y <- as.Date(readline(prompt = "Enter the end date as YYYY-MM-DD."))
trading_volume(x,y)

#Solution
test = data.frame(ETH_USD)
test$Date = as.Date(test$Date,format = "%d-%m-%Y")

trade_assist = function(start_date,end_date){
  if(typeof(start_date) == 'character'|| typeof(end_date) == 'character'){
    print('Please input date value as start date and end date')
  }
  else{
    if(start_date > end_date){
      print('ERROR!! Start date should be before end date')
    }
  else{
    temp = ETH_USD$volume[ETH_USD$Date >= start_date & ETH_USD$Date <= end_date]
    m = round(mean(temp),2)
    s = round(sd(temp),2)
    cv = round(s/m,2)
    tt = list(mean = m,sd = s,cv = paste("The coefficient of variation is:",as.character(cv)))
    print(tt)
    return(tt)
    }
  }
}
```
This will print out NA's in the trading_volume vector when knit into the pdf format as a prompt cannot be entered. But I felt this was a fluid way to make a function that someone could copy and use for this task. 

#Problem 3
#Step 1
```{r}
N = 10000 # Sample size
library(doParallel)
set.seed(112) 
n.cores <- parallel::detectCores() - 1
registerDoParallel(cores=n.cores)

x = rbeta(N, 5, 1)
z = rnorm(N, 10,1)
e = rnorm(N, 10,10)
a = .7
b = .3
c=.6
y = a + b * x + c * z + e

```

#Step 2
```{r}
reg = lm(y ~ x + z)
coef = coef(reg)
cat("The estimated coefficents for a0, a1, and a2 are", round(coef[1],digits=4), "," ,
round(coef[2],digits=4), ", and" ,round(coef[3],digits=4),"respectfully.")
```
#Step 3 
```{r}
B = 10000
bootstrap_coeff = foreach(b =1:B,.combine = 'cbind') %dopar% {
  set.seed(b)
  indices <- sample(N,N,replace = T)
  x1 = x[indices]
  z1 = z[indices]
  y1 = y[indices]
  fit<-lm(y1 ~ x1 + z1)
  fit$coefficients
}
CI = quantile(bootstrap_coeff,c(.025, .975))
cat("The 95% bootstrap confidence interval for the regression coefficients 
is (" , CI[1], "," , CI[2] , ").")
```
#Step 4
```{r}
library(tictoc)
my.cluster <- parallel::makeCluster(n.cores, type = "PSOCK")
doParallel::registerDoParallel(cl = my.cluster)
foreach::getDoParRegistered()
foreach::getDoParWorkers()

tic('Parallel processing')
bootstrap_coeff = foreach(b =1:B,.combine = 'cbind') %dopar% {
  set.seed(b)
  indices <- sample(N,N,replace = T)
  x1 = x[indices]
  z1 = z[indices]
  y1 = y[indices]
  fit<-lm(y1 ~ x1 + z1)
  fit$coefficients
}
toc()
CI = quantile(bootstrap_coeff,c(.025, .975))
cat("The 95% bootstrap confidence interval for the regression coefficients 
is (" , CI[1], "," , CI[2] , ").")

tic('No Parallel processing')
bootstrap_coeff = foreach(b =1:B,.combine = 'cbind') %do% {
  set.seed(b)
  indices <- sample(N,N,replace = T)
  x1 = x[indices]
  z1 = z[indices]
  y1 = y[indices]
  fit<-lm(y1 ~ x1 + z1)
  fit$coefficients
}
toc()
CI = quantile(bootstrap_coeff,c(.025, .975))
cat("The 95% bootstrap confidence interval for the regression coefficients 
is (" , CI[1], "," , CI[2] , ").")

tic('Simple For Loop')
cc = rep(0,B)
for(i in 1:B)
{
  set.seed(b)
  indices <- sample(N[1],N[1],replace = T)
  x1 = x[indices]
  z1 = z[indices]
  y1 = y[indices]
  fit<-lm(y1 ~ x1 + z1)
  cc[i] = fit$coefficients[2]
}
toc()
CI = quantile(bootstrap_coeff,c(.025, .975))
cat("The 95% bootstrap confidence interval for the regression coefficients 
is (" , CI[1], "," , CI[2] , ").")

parallel::stopCluster(cl = my.cluster)
```

So we observe that when using parallel processing we get a much shorter run time when performing the bootstrapping of the coefficients. 
